A Classical Density-Functional Theory for Describing Water Interfaces

### 2013-08-03 papers/water-saft/paper.tex

We first simulate a single hydrophobic rod immersed in water. The
density profile of the water with our functional is compared with that
of Hughes in Fig. \ref{fig:density-single-rod}. The density at contact
with the rods are nearly identical, even more so for larger radius
rods. Since we have changed the association term in the functional, a
difference will occur in the average number of hydrogen bonds in a
given system. We compare the hydrogen bonds with the new and old
functional for rods of a few different radii
(Fig. \ref{fig:single-rod-X}) and find that there is a notable
difference.

@@

We continue our study into three dimensions with a hard sphere solute
in water.\fixme{stuff}.

>>>>

We first simulate a single hydrophobic rod immersed in water. The
density profile of the water with our new functional is compared
agains our previous results in Fig. \ref{fig:density-single-rod}. The
density at contact with the rods are similar and there are slight
difference in density, particularly near the first peak after contact;
all rods we tested exhibited this sharp peak near one diamater form
contact. Since we have changed the association term in the functional,
a difference will occur in the average number of hydrogen bonds. We
compare the hydrogen bonds per length with the new and old functionals
for various rods (shown in Fig. \ref{fig:single-rod-broken-HB}) and
find that there is a noteable difference. The number of broken bonds
both increase linearly with the rod radius, but where this starts
differs between the two methods.

@@

We continue our study into three dimensions with a hard sphere solute
in water. Unlike the single rod, the number of hydrogen bonds does not appear to increase
linearly with the sphere radii we used. \fixme{When the size of
each rodis increase, the surface area increases proportional to radius.
However, when we increase the radius of each sphere, the surface area
increases as $R^2$.}
